BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-02 tex/4-techniques.tex
Add a paragraph to introduce the precisionTable.
Update 4-techniques.tex

Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable architecture illustrated in Figure~\ref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog-post identification} function is able to identify from an URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

Due to space constraints, more precise description and evaluation of these two components where not included in this paper.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:

@@

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.

>>>>

Our crawler is built on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modular architecture illustrated in Figure~\ref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog post identification mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog post pages to search for additional blog posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

Due to space constraints, more precise description and evaluation of these two components where not included in this paper.
\TODO{Again these things are great and you should write a lot more, instead of explaining Javascript rendering so much in 4.1  (it is trivial compared to these nice algorithms).}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
\TODO{merge with 4.3, remove all the usless things. I believe that scalability should be removed from here and included in future work in the end.

Also, everyone knows what scalability is and we don't have a lot of space as we said earlier :)
The Reactive manifesto is not necessary...}
When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:

@@

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.
